Manuscript_Github_Pchabaudi_pir

### 2022-07-29 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_pirAnalysis.Rmd
Improved all pir stacked bar chart plot, accidentally may have altered the ancestral bar chart

(
  p <- ggplot(data = cir_plot, 
              aes(x = time, 
                  y = sum_tpm,
                  fill = transmission)) +
    stat_summary(fun.y = median, fun.ymin = median, fun.ymax = median,
                 geom = "bar", width = 0.75, size = 0.25, position = 'dodge') +
    scale_y_continuous(breaks = y_scale) +
    scale_fill_manual(values = cbPalette) +
    geom_point(stat = 'identity', position = position_dodge(width = 0.75)) +
    ylab(as.expression(bquote('Total ancestral '~italic(.('pir'))~'TPM'))) +
    xlab('Asexual blood stage development cycle') +
    theme_classic() +
    theme(axis.text.x=element_text(angle = 0, 
                                   vjust = 0.5,
                                   size = 10))
)

@@

(
  p <- ggplot(data = cir_plot, 
              aes(x = factor(time), 
                  y = tpm,
                  fill = factor(SorL))) +
    geom_col(colour = 'black',
             size = 0.1,
             position = 'stack') +
    scale_y_continuous(breaks = y_scale) +
    scale_fill_manual(values = SorL_col) +
    ylab(as.expression(bquote('Total '~italic(.('pir'))~'TPM'))) +
    xlab('Asexual blood stage development cycle') +
    theme_classic() +
    theme(axis.text.x=element_text(angle = 90, 
                                   vjust = 0.5,
                                   size = 7)) +
    facet_grid(~transmission, scales = 'free')
)

if(global_save_var){
  ggsave(filename = 'plots/allPir_BarChart.pdf',
          plot = p,
          dpi = 300,
          width = 20,
          height = 10,
          units = 'cm')
}

>>>>

(
  p <- ggplot(data = cir_plot, 
              aes(x = time, 
                  y = sum_tpm,
                  fill = transmission)) +
    stat_summary(fun.y = median, fun.ymin = median, fun.ymax = median,
                 geom = "bar", width = 0.75, size = 0.25, position = 'dodge') +
    scale_y_continuous(breaks = y_scale) +
    scale_fill_manual(values = cbPalette) +
    geom_point(stat = 'identity', position = position_dodge(width = 0.75)) +
    ylab(as.expression(bquote('Total ancestral '~italic(.('pir'))~'TPM'))) +
    xlab('Asexual blood stage development cycle') +
    theme_classic() +
    theme(axis.text.x=element_text(angle = 0, 
                                   vjust = 0.5,
                                   size = 12))
)

@@

(
  p <- ggplot(data = cir_plot, 
              aes(x = factor(time), 
                  y = tpm,
                  fill = factor(SorL))) +
    geom_col(colour = 'black',
             size = 0.1,
             position = 'stack') +
    scale_y_continuous(breaks = y_scale) +
    scale_fill_manual(values = SorL_col) +
    ylab(as.expression(bquote('Total '~italic(.('pir'))~'TPM'))) +
    xlab('Asexual blood stage development cycle') +
    theme_classic() +
    guides(fill = guide_legend(title = 'Subfamily')) +
    theme(axis.text.x=element_text(angle = 90, 
                                   vjust = 0.5,
                                   size = 10),
          axis.text.y = element_text(size = 12),
          axis.title.y = element_text(size = 15),
          axis.title.x = element_text(size = 15),
          strip.text = element_text(size = 15)) +
    facet_grid(~transmission, scales = 'free')
)

if(global_save_var){
  ggsave(filename = 'plots/allPir_stackedBarChart.pdf',
          plot = p,
          dpi = 300,
          width = 20,
          height = 20,
          units = 'cm')
}
